\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{url}
\usepackage{hyperref}
\urlstyle{tt}

\title{Physical Promotion Attempt From Finite-Capacity Causal Networks}
\author{Abraham Greenman}
\date{2026}

\begin{document}
\maketitle

\begin{abstract}
This paper closes Paper 17 in the finite-capacity causal-network theorem
ladder. Starting from the closed Paper 16 conditional external review and
reproduction certificates theorem, it constructs a finite, network-native
physical-promotion attempt interface. The construction is conditional and
non-promoting: it defines attempt records, eligibility references, evidence
bundle references, review certificate references, decision rows, objection
rows, residual-risk rows, stability rows, audit rows, rollback rows, and a
final conditional certificate. It does not prove physical promotion attempt
success, physical promotion, physical validation, empirical adequacy, review
acceptance, reproduction success, benchmark success, prediction success,
falsification success, physical nature realization, or a unified field theory.
\end{abstract}

\section{Theorem Status}

The Paper 17 theorem is closed as a conditional finite interface theorem. The
formal Lean endpoint is:
\begin{quote}
\texttt{paper17\_ppa008\_final\_conditional\_certificate\_closes}\\
\texttt{physical\_promotion\_attempt\_theorem}
\end{quote}
The closing contract is:
\begin{quote}
\path{Paper17PhysicalPromotionAttemptTheoremContract.closed}
\end{quote}

The Rust audit surface is in \path{rust/cclab_accel/src/lib.rs}, and the
regression tests are in
\path{rust/cclab_accel/tests/physical_promotion_attempt.rs}. The
required local checks are:
\begin{verbatim}
make test-fast
make lean-build
\end{verbatim}

\section{Upstream Assumption}

Paper 17 starts after the frozen Paper 16 result:
\begin{itemize}
\item Paper 16 commit:
\path{8bb266493b1c53c776b2d39a47140794edc8935f}.
\item Paper 16 formal endpoint:
\path{Paper16ExternalReviewReproductionCertificatesTheoremContract.closed}.
\item Paper 16 canonical proof:
\path{paper16_errc008_final_conditional_certificate_closes_external_review_reproduction_certificates_theorem}.
\end{itemize}

The upstream result is consumed only as a conditional review/reproduction
certificate package. It is not reinterpreted as review acceptance,
reproduction success, external validation success, physical promotion, or
physical nature realization.

\section{Main Theorem}

\textbf{Theorem.} Starting from the closed Paper 16 conditional external
review and reproduction certificates theorem, there is a finite,
network-native physical-promotion attempt interface preserving finite
capacity, locality, bounded transfer, Paper 16 certificate compatibility,
stability, auditability, rollback behavior, and no-hidden-import boundaries.
The interface closes only as a conditional attempt-interface theorem and does
not close any physical-promotion, physical-validation, success, physical
nature, or unified-field claim.

\section{Construction}

The construction is a sequence of eight closed rungs.

\subsection{PPA-001: Upstream Binding}

PPA-001 binds Papers 1--16 through frozen upstream commits and the Paper 16
final conditional certificate. The rung preserves finite capacity, locality,
bounded transfer, and the claim boundary. No physical promotion, validation,
empirical adequacy, review acceptance, reproduction success, physical nature,
or unified-field claim is imported.

\subsection{PPA-002: Finite Attempt Records}

PPA-002 defines the physical-promotion attempt record as a bounded,
auditable interface row. Each row contains finite labels for:
\begin{itemize}
\item attempt identifier,
\item eligibility reference,
\item evidence-bundle reference,
\item review-certificate reference,
\item decision reference,
\item objection reference,
\item residual-risk reference,
\item audit-status descriptor.
\end{itemize}
The row is an attempt record only. It does not assert attempt success,
promotion, validation, empirical adequacy, acceptance, reproduction success,
benchmark success, prediction success, falsification success, simulation-only
promotion, fit-only calibration, physical nature, or unified-field promotion.

\subsection{PPA-003: Eligibility, Evidence, and Review Descriptors}

PPA-003 refines the attempt row with finite eligibility, evidence-bundle, and
review-reference descriptors. Eligibility descriptors are not eligibility
success findings. Evidence descriptors are not evidence sufficiency claims.
Review references are not review acceptance claims. Paper 16 certificate
references remain reference-only.

\subsection{PPA-004: Decision, Objection, and Residual-Risk Descriptors}

PPA-004 defines finite decision, objection, and residual-risk descriptors.
Decision descriptors are not promotion decisions. Objection descriptors are
not objection adjudications or review outcomes. Residual-risk descriptors are
not risk discharge claims. These descriptors are bounded, auditable, local to
the attempt interface, and rollback-compatible.

\subsection{PPA-005: Paper 16 Certificate Compatibility}

PPA-005 defines compatibility rows for the frozen Paper 16 endpoint and final
certificate. The compatibility rows record finite references to review and
reproduction certificates without asserting review acceptance, reproduction
success, validation success, benchmark success, prediction success, or
falsification success.

\subsection{PPA-006: Stability, Audit, and Rollback}

PPA-006 defines finite stability, audit, and rollback descriptors. Stability
is interface stability only, not empirical stability. Audit descriptors are
finite and replayable from attempt rows. Rollback is local bookkeeping for the
attempt interface and is not falsification success, review failure, promotion
failure, validation failure, or empirical inadequacy.

\subsection{PPA-007: No-Hidden-Import Audit}

PPA-007 closes a fail-closed audit for hidden imports. The audit rejects
hidden physical-promotion attempt success, physical promotion, physical
validation, empirical adequacy, review acceptance, reproduction success,
benchmark success, prediction success, falsification success, simulation-only
promotion, fit-only calibration, physical nature realization, and
unified-field-theory imports. Closing this audit establishes absence of those
hidden imports only; it does not promote or validate the attempt.

\subsection{PPA-008: Final Conditional Certificate}

PPA-008 assembles the final certificate. It consumes the closed contracts for
PPA-001 through PPA-007 and closes
\path{Paper17PhysicalPromotionAttemptTheoremContract.closed}. The closing
certificate is conditional and interface-level. It preserves finite capacity,
locality, bounded transfer, the hidden-import audit, and every non-promotion
boundary.

\section{Proof}

The proof is by finite contract assembly. For each rung, the Lean development
defines a contract whose \path{closed} predicate is a finite conjunction of
its required fields. A canonical contract instantiates each field with the
corresponding boundedness, compatibility, audit, or no-claim witness. Lean then
proves each canonical rung closed by unfolding the contract and simplifying.

The final theorem contract contains the closed status of PPA-001 through
PPA-008 plus the non-promotion boundary fields. The theorem:
\begin{quote}
\texttt{paper17\_ppa008\_final\_conditional\_certificate\_closes}\\
\texttt{physical\_promotion\_attempt\_theorem}
\end{quote}
unfolds the final contract, unfolds the canonical rung witnesses, and closes
the conjunction. Therefore the Paper 17 theorem is closed exactly as a
conditional finite physical-promotion attempt interface theorem.

\section{Runtime Audit}

The Rust guard mirrors the formal ladder. Each rung has a canonical runtime
record and a \path{closes_ppa00n} predicate. The final runtime certificate
requires:
\begin{itemize}
\item all descriptors are bounded,
\item the Paper 16 endpoint and final certificate match the frozen references,
\item every compatibility row is reference-only,
\item rollback is local bookkeeping,
\item the hidden-import audit rejects all forbidden claims,
\item all physical-promotion and success claims remain false.
\end{itemize}
The final runtime certificate closes the Paper 17 theorem contract only when
all rung predicates close and the non-promotion boundary remains false for all
forbidden claim fields.

\section{Claim Boundary}

This theorem does not prove any of the following:
\begin{itemize}
\item physical promotion attempt success,
\item physical promotion,
\item physical validation,
\item empirical adequacy,
\item review acceptance,
\item reproduction success,
\item benchmark success,
\item prediction success,
\item falsification success,
\item observed particle catalog recovery,
\item physical Standard Model recovery,
\item physical particle excitation recovery,
\item physical matter-field recovery,
\item physical gauge-field recovery,
\item physical quantum dynamics,
\item continuum quantum field theory,
\item simulation-only promotion,
\item fit-only calibration,
\item physical nature realization,
\item unified field theory.
\end{itemize}

\section{Reproducibility}

The theorem can be checked locally from the repository root:
\begin{verbatim}
make test-fast
make lean-build
\end{verbatim}
The Lean proof is located at
\path{GPD/formal/FiniteCapacity/PhysicalPromotionAttempt.lean}. The Rust
guard is located at \path{rust/cclab_accel/src/lib.rs}. The regression tests
are located at
\path{rust/cclab_accel/tests/physical_promotion_attempt.rs}.

\section{Conclusion}

Paper 17 closes the finite physical-promotion attempt interface theorem. It
provides a bounded, auditable, rollback-compatible, certificate-compatible
attempt structure downstream of Paper 16. The closure is intentionally narrow:
it closes the existence and compatibility of the finite attempt interface, not
promotion success, validation success, empirical adequacy, physical nature
realization, or unified-field promotion.

\end{document}
